---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)
library(primer3)
```

# primer3

primer3 provides a direct interface to the thermodynamic
  calculations in Primer3 (melting temperatures, primer dimers, secondary
  structures, etc.). The package is self-contained and does not require a
  separate installation of Primer3.

## Overview

primer3 contains four functions:

```{r eval=FALSE}
calculate_tm()
calculate_hairpin()
calculate_homodimer()
calculate_dimer()
```

See the function documentation for details on inputs and usage.

## Installation
```{r, eval = FALSE}
# Install the latest version directly from GitHub
install.packages("devtools")
devtools::install_github("jensenlab/primer3")
```

## Usage
```{r}
calculate_tm(c("AAGCCGCGTACGA", "AAGAGCGATGACG"))

calculate_hairpin("CCCCCATCCGATCAGGGGG")
```

## Acknowledgements

primer3 builds on [Primer3](http://primer3.sourceforge.net) and modifications
made by the [primer3-py](https://github.com/libnano/primer3-py) project.

